Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-26 TACAS2018/paper.tex
Control Theory appendix

\newcommand{\jrronly}[1]{{}}
\newcommand{\mat}[1]{\boldsymbol{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
%\newtheorem{theorem}{Theorem}
%\newtheorem{corollary}{Corollary}
%\newtheorem{proof}{Proof}

@@

 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsection{Accelerated dynamics for systems without inputs}\label{sec:real_discrete_no_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 Given a specific time $T$, the state $\vec{x}_T$ present at $T$ can be expressed as a linear function of $\vec{x}_0$ as described below. Note that, as the system has no inputs, its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.

@@

\begin{theorem}
The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic noise signal upperbound by 
\begin{align}
|\vec{y}_{k}-{\vec{y}_{t_d}}_{k}|_1 \leq q_t, \text{ where } q_t=&(|\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})|_1+|\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}|_1)|U|_\infty
\end{align}
where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$.
\end{theorem}
%
\todo{notation $| |_x$ ?}
%
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Errors generated by the numerical representation} 
\label{sec:numeric_rep}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

Let us first consider the effect of the quantization errors. 
Within the controller, state values are manipulated at low precision.
%alongside the vector multiplication $\mat{K}\vec{x}$.
Furthermore, the quantizers for the DAC and the ADC introduce truncation errors
which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
and $\mathcal{F}_{\langle A \rangle}$, respectively. Finally, let us call $\vec{\nu}_e$ the
error caused by the FWL effects on the observer
\todo{the observer was not defined..}
(\emph{i.e} the numerical errors 
in the calculations as opposed to the estimation error).
The inputs are computed using the following equation: 
%
\begin{align}
u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
\label{eq:uk}
\end{align}

@@

We want the state space dynamics in reachable form ($\mat{A}_c$) and the observer error dynamics in observable form ($\mat{A}_o$), i.e. with dynamics whose coefficients are represented solely by those of the characteristic polynomial as follows:
\begin{align*}
\mat{A}_{c}=\left[
\begin{array}{cc}
k_n-a_n&\begin{array}{cc}\cdots&k_1-a_1\end{array}\\
\mat{I}&\mat{0}
\end{array}\right]&&
\mat{A}_{o}=\left[
\begin{array}{ccc}
a_n-l_n&&\mat{I}\\
&&\vdots\\
a_1-l_1&&\mat{0}
\end{array}\right]
\end{align*}
where $\sum_{i=0}^p a_iz^i$ is the characteristic polynomial of the plant.
This is achieved by the following transformation. Let
\begin{equation}
\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
\end{equation}
We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\mat{B}' \vec{r}_k
+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
\nonumber\\
\vec{y}_k
=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_cf}
\end{align}
{%\setlength{\belowdisplayskip}{0pt}
\begin{align*}
\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}_d\right)\mat{T}_o^{-1}\\
\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}\mat{T}_o^{-1}\\
\mat{B}'=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]\\
\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{C}_t=&\mat{C}_d\mat{T}_c&
\mat{L}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
\end{align*}
}

@@

Careful examination of the above matrices reveals that because the $\mat{A}'$ is
upper block diagonal, the spectrum of $\mat{A}'$ is equal to the union of
the spectrum of $\mat{A}_{c}$ and $\mat{A}_{o}$, which can be calculated
separately.  In other words, the characteristic polynomial of the closed loop is
equal to the multiplication of the characteristic polynomials of the controller
and the observer when seen independently.
%
\begin{align*}
P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=1}^p{(a_i-k_i)z^{p-i}}\right) \left(z^p+\sum_{i=1}^p{(l_i-a_i)z^{p-i}}\right)
\end{align*}

@@

In this section, we assume that the observer model is further discretised in
the value domain, i.e., the domain for both
the controller and the observer is $\mathbb{R}_{\langle C \rangle}$.
%% While in the previous section, we assumed that
%% ${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization, in this section
%% we take into consideration the numerical representation and namely
%% Thus far we looked at checking stability
%% %have presented a verification procedure for
%% of a continuous plant in discretized time domain (i.e., the range of the quatizers is still
%% $\mathbb{R}$).  The next step we must realize is that the controller and the
%% observer exist in a digital program, hence their domain is
%% $\mathbb{R}_{\langle C \rangle}$.
%
%% This has two separate effects on the
%% model.  If we recall Equation~\eqref{eq:observer_LTI}, the matrices of the observer
%% and the controller are not necessarily those of the plant.  In fact we have
%% $\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$,
This means that we have 
${\mat{A}_d}_{\langle C
\rangle},{\mat{B}_d}_{\langle C \rangle},{\mat{C}_d}_{\langle C \rangle},
\mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \in
\mathbb{R}_{\langle C \rangle}^*$ where $*$ represents the appropriate
dimension for each matrix.  Unfortunately this means that although combined
matrices such as $\mat{A}_t$ are in the reals, they suffer from the fixed
word restrictions in their composing matrices.

When our observer is implemented using a finite precision controller, new
problems arise due to the FWL effects.  Let ${\mat{A}_d}_{\langle C
\rangle}$, ${\mat{B}_d}_{\langle C \rangle}$ and ${\mat{C}_d}_{\langle C
\rangle}$ be the dynamics represented in $\mathbb{R}_{\langle C\rangle}^*$,
%
%and $\mat{A}_e=\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}$, $\mat{B}_e=\mat{B}_d-{\mat{B}_d}_{\langle C \rangle}$,
%and $\mat{C}_e=\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}$ their corresponding errors.  
Equation \eqref{eq:observer_LTI_cf} becomes:
%
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\mat{B}_{c} \vec{r}_k
+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
\vec{y}_k=&\mat{C}_{t}\vec{x}_k'% + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_FWL_cf}
\end{align}
where
{\setlength{\abovedisplayskip}{2pt}
\setlength{\belowdisplayskip}{2pt}
\begin{align*}
\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
\mat{A}_{o}=&\mat{T}_o\left({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}{\mat{C}_d}_{\langle C \rangle}\right)\mat{T}_o^{-1}\\
\mat{B}_{o}=&\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}&
\mat{B}_{e}=&\mat{T}_c(\mat{B}_d-{\mat{B}_d}_{\langle C \rangle})\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}\\
\mat{A}_{e}=&\mat{T}_o\left(\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_e\right)\mat{T}_o^{-1}&
\mat{C}_{e}=&\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}\\
\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{C}_t=&\mat{C}_d\mat{T}_c&
\mat{L}_{\langle C \rangle}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
\end{align*}
}
{\setlength{\abovedisplayskip}{0pt}
\begin{align*}
\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]&
\mat{B}_{c}=&\left[\begin{array}{c}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]
\end{align*}
}
The first effect of this new equation is that $\mat{A}'$ is no longer upper
diagonal.  We must therefore compensate for the errors introduced in order
to find a stable solution.  We can use Gershgoring \todo{citation} disks to limit the error
in the expected eigenvalues.  Let $\delta_o=\max(|{\mat{A}_e}_{i,*}|_2)$
(\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound
for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in [1, n],
|{\lambda_o}_{i}-\hat{\lambda_o}_{i}|<\delta_o$,where ${\lambda_o}_{i}$ are the
true eigenvalues of the observer and $\hat{\lambda_o}_{i}$ the eigenvalues of
the perturbed observer.  We note that in the case of stability we only care
about the error with respect to the unit circle, which is equivalent to
upper bounding the estimation of the largest eigenvalue.  Hence, given a
desired upper value $\overline{\lambda}$, we apply Jury's criterion on the
polynomial.
%
\begin{equation}
P_o'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j : \overline{\lambda'}=(1+\delta_o)\overline{\lambda}
\end{equation}
%
In the case of the reachable eigenvalues, the procedure is the same except
that we obtain our bound $\delta_c=\max(|{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}|_2)$
(\emph{i.e.} the largest column norm in $ \left[\begin{array}{c}\mat{A}_e\\ \mat{B}_e\end{array}\right]$) and
apply Jury's Criterion over
%
\begin{equation}
P_r'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j : \overline{\lambda'}=(1+\delta_c)\overline{\lambda}
\end{equation}

@@

%-------------------------------
\subsection{Results}
\label{exp:results}
%-------------------------------
The technique was applied  to the benchmarks and the results can be seen in table \ref{tab:results}
\begin{table}
\centering
%
\begin{tabular}{| r | l | c | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order}  & \multicolumn{1}{|c|}{$\mat{K}$} & \multicolumn{3}{|c|}{$\mat{K}+\mat{L}+T_s$} \\
   &                                  & & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max}\\\hline
1  & DC Motor          & 2 & 2.1\,s& 16,16  &   4.1\,s &   4.1\,s\\
2  & Helicopter        & 3  & 1.4\,s& 8.6\,s  &   54.9\,s &   t.o.\\
3  & Inverted Pendulum & 4 &   0.6\,s& 16,24  &  308.4\,s &  308.4\,s\\
4  & Magnetic Pointer  & 2  & 44.1\,s& 24,16  &  7.7\,s &  7.7\,s \\
%5  & Magnetic Suspension & 2 & 0.6\,s& 16,24  &   0\,s &   0\,s\\
5  & Pendulum          & 2 & 14.0\,s& 16,16  &   3.4\,s &   3.4\,s\\
6  & Suspension        & 2 & 73.7\,s& 16,24  &   1316.2\,s &   1316.2\,s\\
7  & Tape Driver       & 3 & 68.3\,s& 16,24  &   57.8\,s &   57.8\,s\\
%9 & Satellite          & 2 &   0.7\,s& - &  - &  -\\ %unobservable
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table}

@@

>>>>

\newcommand{\jrronly}[1]{{}}
\newcommand{\mat}[1]{\boldsymbol{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
%\newtheorem{theorem}{Theorem}
%\newtheorem{corollary}{Corollary}
%\newtheorem{proof}{Proof}
\newtheorem{assumption}{Assumption}

@@

 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsection{Accelerated dynamics for continuous time systems without inputs}\label{sec:real_discrete_no_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 Given a specific time $T$, the state $\vec{x}_T$ present at time $T$ can be expressed as a linear function of $\vec{x}_0$ as described below. Note that, as the system has no inputs, its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.

@@

\begin{theorem}
The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic noise signal upperbound by 
\begin{align}
|\vec{y}_{k}-{\vec{y}_{t_d}}_{k}|_\infty \leq q_t, \text{ where } q_t=&(|\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})|_1+|\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}|_1)|U|_\infty
\end{align}
where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$.
\end{theorem}
%
\todo{notation $| |_x$ ?}
%
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Errors generated by the numerical representation} 
\label{sec:numeric_rep}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

Let us first consider the effect of the quantization errors. 
Within the controller, state values are manipulated at low precision.
Furthermore, the quantizers for the DAC and the ADC introduce truncation errors
which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
and $\mathcal{F}_{\langle A \rangle}$, respectively. Finally, let us call $\vec{\nu}_e$ the
error caused by the FWL effects on the observer
\todo{the observer was not defined..}
(\emph{i.e} the numerical errors 
in the calculations as opposed to the estimation error).
The inputs are computed using the following equation: 
%
\begin{align}
u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
\label{eq:uk}
\end{align}

@@

We want the state space dynamics in reachable form ($\mat{A}_c$) and the observer error dynamics in observable form ($\mat{A}_o$), i.e. with dynamics whose coefficients are represented solely by those of the characteristic polynomial as follows:
\begin{align*}
\mat{A}_{c}=\left[
\begin{array}{cc}
k_{p-1}-a_{p-1}&\begin{array}{cc}\cdots&k_0-a_0\end{array}\\
\mat{I}&\mat{0}
\end{array}\right]&&
\mat{A}_{o}=\left[
\begin{array}{ccc}
l_{p-1}-a_{p-1}&&\mat{I}\\
&&\vdots\\
l_0-a_0&&\mat{0}
\end{array}\right]
\end{align*}
where $\sum_{i=0}^p a_iz^i$ is the characteristic polynomial of the plant and $a_p=1$.
This is achieved by the following transformation. Let
\begin{equation}
\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
\end{equation}
We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\mat{B}' \vec{r}_k
+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
\nonumber\\
\vec{y}_k
=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_cf}
\end{align}
{%\setlength{\belowdisplayskip}{0pt}
\begin{align*}
\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}_d\right)\mat{T}_o^{-1}\\
\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}\mat{T}_o^{-1}\\
\mat{B}'=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]\\
\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{C}_t=&\mat{C}_d\mat{T}_c&
\mat{L}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
\end{align*}
}

@@

Careful examination of the above matrices reveals that because the $\mat{A}'$ is
upper block diagonal, the spectrum of $\mat{A}'$ is equal to the union of
the spectrum of $\mat{A}_{c}$ and $\mat{A}_{o}$, which can be calculated
separately.  In other words, the characteristic polynomial of the closed loop is
equal to the multiplication of the characteristic polynomials of the controller
and the observer when seen independently.
%
\begin{align*}
P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(l_i-a_i)z^{i}}\right)
\end{align*}

@@

In this section, we assume that the observer model is further discretised in
the value domain, i.e., the domain for both
the controller and the observer is $\mathbb{R}_{\langle C \rangle}$.
%% While in the previous section, we assumed that
%% ${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization, in this section
%% we take into consideration the numerical representation and namely
%% Thus far we looked at checking stability
%% %have presented a verification procedure for
%% of a continuous plant in discretized time domain (i.e., the range of the quatizers is still
%% $\mathbb{R}$).  The next step we must realize is that the controller and the
%% observer exist in a digital program, hence their domain is
%% $\mathbb{R}_{\langle C \rangle}$.
%
%% This has two separate effects on the
%% model.  If we recall Equation~\eqref{eq:observer_LTI}, the matrices of the observer
%% and the controller are not necessarily those of the plant.  In fact we have
%% $\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$,
This means that we have 
${\mat{A}_d}_{\langle C
\rangle},{\mat{B}_d}_{\langle C \rangle},{\mat{C}_d}_{\langle C \rangle},
\mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \in
\mathbb{R}_{\langle C \rangle}^*$ where $*$ represents the appropriate
dimension for each matrix.  Unfortunately this means that although combined
matrices such as $\mat{A}_c$ are in the reals, they suffer from the fixed
word restrictions in their composing matrices.

When our observer is implemented using a finite precision controller, new
problems arise due to the FWL effects.  Let ${\mat{A}_d}_{\langle C
\rangle}$, ${\mat{B}_d}_{\langle C \rangle}$ and ${\mat{C}_d}_{\langle C
\rangle}$ be the dynamics represented in $\mathbb{R}_{\langle C\rangle}^*$,
%
%and $\mat{A}_e=\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}$, $\mat{B}_e=\mat{B}_d-{\mat{B}_d}_{\langle C \rangle}$,
%and $\mat{C}_e=\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}$ their corresponding errors.  
Equation \eqref{eq:observer_LTI_cf} becomes:
%
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\mat{B}_{c} \vec{r}_k
+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
\vec{y}_k=&\mat{C}_{t}\vec{x}_k'% + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_FWL_cf}
\end{align}
where
{\setlength{\abovedisplayskip}{2pt}
\setlength{\belowdisplayskip}{2pt}
\begin{align*}
\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
\mat{A}_{o}=&\mat{T}_o\left({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}{\mat{C}_d}_{\langle C \rangle}\right)\mat{T}_o^{-1}\\
\mat{B}_{o}=&\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}&
\mat{B}_{e}=&\mat{T}_c(\mat{B}_d-{\mat{B}_d}_{\langle C \rangle})\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}\\
\mat{A}_{e}=&\mat{T}_o\left(\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_e\right)\mat{T}_o^{-1}&
\mat{C}_{e}=&\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}\\
\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{C}_t=&\mat{C}_d\mat{T}_c&
\mat{L}_{\langle C \rangle}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
\end{align*}
}
{\setlength{\abovedisplayskip}{0pt}
\begin{align*}
\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]&
\mat{B}_{c}=&\left[\begin{array}{c}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]
\end{align*}
}
The first effect of this new equation is that $\mat{A}'$ is no longer upper
diagonal.  We must therefore compensate for the errors introduced in order
to find a stable solution.  We can use Gershgoring disks~\cite{van1996matrix} to limit the error
in the expected eigenvalues.  Let $\delta_o=\max(|{\mat{A}_e}_{i,*}|_2)$
(\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound
for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in [1, n],
|{\lambda_o}_{i}-\hat{\lambda_o}_{i}|<\delta_o$,where ${\lambda_o}_{i}$ are the
true eigenvalues of the observer and $\hat{\lambda_o}_{i}$ the eigenvalues of
the perturbed observer.  We note that in the case of stability we only care
about the error with respect to the unit circle, which is equivalent to
upper bounding the estimation of the largest eigenvalue.  Hence, given a
desired upper value $\overline{\lambda}$, we apply Jury's criterion on the
polynomial.
%
\begin{equation}
P_o'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j : \overline{\lambda'}=(1+\delta_o)\overline{\lambda}
\end{equation}
%
In the case of the reachable eigenvalues, the procedure is the same except
that we obtain our bound $\delta_c=\max(|{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}|_2)$
(\emph{i.e.} the largest column norm in $ \left[\begin{array}{c}\mat{A}_e\\ \mat{B}_e\end{array}\right]$) and
apply Jury's Criterion over
%
\begin{equation}
P_r'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j : \overline{\lambda'}=(1+\delta_c)\overline{\lambda}
\end{equation}

@@

%-------------------------------
\subsection{Results}
\label{exp:results}
%-------------------------------
The technique was applied  to the benchmarks and the results can be seen in table \ref{tab:results}
\begin{table}
\centering
%
\begin{tabular}{| r | l | c | c | c | r | r | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order} & \multicolumn{1}{|c|}{count} & \multicolumn{1}{|c|}{$\mat{K}$} & \multicolumn{3}{|c|}{$\mat{K}+\mat{L}+T_s$} \\
   &                                 & & & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max}\\\hline
1  & DC Motor          & 2 & 433 & 2.1\,s& 3.5\,s &   6.9\,s &   20.7\,s\\
2  & Helicopter        & 3  & 54 & 1.4\,s& 8.8\,s  &   33.5\,s & 160.3\,s\\
3  & Inverted Pendulum & 4 & 1 &   0.6\,s& 16,24  &  308.4\,s &  308.4\,s\\
4  & Magnetic Pointer  & 2  & 246 & 44.1\,s& 7.7\,s  &  36.9\,s &  184.6\,s \\
%5  & Magnetic Suspension & 2 & 1 & 0.6\,s& 16,24  &   0\,s &   0\,s\\
5  & Pendulum          & 2 & 432 & 14.0\,s& 3.4\,s  &   26.9\,s &   156.8\,s\\
6  & Suspension        & 2 & 1 & 73.7\,s& 16,24  &   1316.2\,s &   1316.2\,s\\
7  & Tape Driver       & 3 & 488 & 68.3\,s& 12.4\,s  &   37.2\,s &   185.3\,s\\
%9 & Satellite          & 2 & 1 &   0.7\,s& - &  - &  -\\ %unobservable
   & Total                 &   & 1645 & & 3.4\,s & 20.1\,s & 1316.2 \,s\\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table}

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Control Theory} \label{sec:control_theory}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

Since our models are being applied to linear control systems, and in particular to feedback systems with observers,
we provide a summary of the important elements using control theory for their transfromations.

%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%\subsection{Static Output Feedback and Pole Placement} \label{sec:pole_place}
%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%\begin{figure*}[htb]
%\centering
%\tikzset{add/.style n args={4}{
%    minimum width=6mm,
%    path picture={
%        \draw[circle] 
%            (path picture bounding box.south east) -- (path picture bounding box.north west)
%            (path picture bounding box.south west) -- (path picture bounding box.north east);
%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
%        }
%    }
% }
%\resizebox{1.0\textwidth}{!}{
% \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
%     semithick, initial text=, ampersand replacement=\&,]
%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
%    \node[draw=none] (r) {$R(z)$};
%%   \& \coordinate (aux0);
%   \& \node[circle,add={-}{+}{}{}] (circle) {};
%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
%   \& \node[rectangle,draw,
%	minimum width=1cm,
%	minimum height=1cm,
%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
%   \& complexnode/.pic={ 
%      \node[rectangle,draw,
%	minimum width=3cm,
%	minimum height=1.6cm,
%	label=\textbf{DAC},] (dac) {};
%     \node[circle,add={}{+}{+}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
%     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
%     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
%     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}   
%   \& \node[rectangle,draw,
%	minimum width=1cm,
%	minimum height=1cm,
%        label=\textbf{Plant}] (gs) {{\sc $G(s)$}};
%   \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};
